---
title: "Lab 7 Multiple Linear Regression intro"
author: "Katherine Rosencrance"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```


## Explore penguins

Use `GGally::ggpairs()` to create a pairs plot

```{r}
ggpairs(penguins)
```

Thats overkill. Lets simplify the variables we include in our ggpairs plot

-species
-bill_length_mm through body_mass_g

```{r}
penguins %>%
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple linear regression

We are going to understand better the realtionships between multiple predictor variables and an outcome which is penguin body mass

the different predictor variables are

-species
-flipper length
-sex
-bill depth

### Model 1

Model body mass based on only fliper l and bill d (bad idea)
```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

model_1

# More info on coefficients and model
summary(model_1)
```
If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass increases by 51.54 g on average.

R squared number means 76% of variance in body mass is explained by this model (penguin flipper length and bill depth)

Actually we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species+sex, data = penguins)

model_2

# Try interpreting coefficients for flipper length, gentoo, and male

# Flipper length- if everythig else constant, on average youd expect a male to be 530 g larger than females

# Gentoo - if everything else constant, youd expect a gentoo penguin to be 836 g larger in body mass than adelie on avergae


```
reference level = if not shown!


### Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_point(aes(color = species))+ 
  facet_wrap (~ sex)
```

## A couple ways to get and report MLR model outcomes

use broom::tidy to get coefficient data

```{r}
penguin_model2<- tidy(model_2)
```

in line code that spits out coefficient for gentoo `r penguin_model2$estimate[4]`

## look a mdel diagnostics

use plot() function

```{r}
plot(model_2)
```

## Report model outputs in a summary table

use model summary

```{r}
modelsummary(model_2)
```
use stargazer

```{r, results = "asis"}
stargazer(model_2, type = "html")
```



